\documentclass[a4paper,10pt]{article}
\usepackage{url}


%opening
\title{Examples for the Library baNaNa talk}
\author{SIAM Student Chapter TU Delft}

\begin{document}

\maketitle

\begin{abstract}
From time to time, it can be difficult to find a reference especially if it is old, expensive, not-in-english, very new, etc..
In this document, we propose some references to be used as examples during the baNaNa talk "Many ways to find your reference" by Nicole Potters.
\end{abstract}
\begin{itemize}
 \item Article: W. E. Arnoldi, "The principle of minimized iterations in the solution of the matrix eigenvalue problem," Quarterly of Applied Mathematics, volume 9, pages 17--29, 1951.
\item Article: Gu G.-D., Zhou, X.-L., and Lin L., "A Flexible preconditioned Arnoldi method for shifted Linear Systems", Journal of Computational Mathematics, Vol.25, No.5, 2007, 522-530.
\item Book: Krylov Subspace Methods: Principles and Analysis", J\"{o}rg Liesen and Zdenek Strakos, Oxford University Press. 2012, 408 pages.
\item Online book: 

\url{http://delft.eblib.com/patron/FullRecord.aspx?p=454286}. 

How to download? Cannot open link?
\item Journal: Mathematical Models and Methods in Applied Sciences: we do not have access to his journal
but how to get a copy of an article of this journal?, example: \\
            
    MODELING CROWD DYNAMICS FROM A COMPLEX SYSTEM VIEWPOINT \\
    NICOLA BELLOMO, BENEDETTO PICCOLI, ANDREA TOSIN \\
    Mathematical Models and Methods in Applied Sciences Vol. 22, (2012) \\

 \end{itemize}




\end{document}
